cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Initial work on multiple cluster examples

The main function of the package is `gen_multicluster()`. This function generates clusters of various shapes, allowing users to specify the number of samples in each cluster, as well as their locations, scaling, and rotations across specific dimensions. Additionally, users can add background noise into the generated data by using the `is_bkg` option.

@@

```{r}
main_tb <- tibble(arg = c("n",
                            "p",
                            "k",
                            "loc",
                            "scale",
                            "shape",
                            "rotation",
                            "is_bkg"), 
                        exp = c("A numeric vector representing the sample sizes.",
                                "A numeric value representing the number of dimensions.",
                                "A numeric value representing the number of clusters.",
                                "A numeric matrix representing the locations/centroids of clusters.",
                                "A numeric vector representing the scaling factors of clusters.",
                                "A character vector representing the shapes of clusters.",
                                "A numeric list which contains plane and the corresponding angle along that plane for each cluster.",
                                "A Boolean value representing the background noise should exist or not."))
```

@@

### Odd shapes

Add table of odd shapes..

>>>>

The main function of the package is `gen_multicluster()`. This function generates clusters of various shapes, allowing users to specify the number of points in each cluster, as well as their locations, scaling, and rotations across specific dimensions. Additionally, users can add background noise into the generated data by using the `is_bkg` option.

@@

```{r}
main_tb <- tibble(arg = c("n",
                            "p",
                            "k",
                            "loc",
                            "scale",
                            "shape",
                            "rotation",
                            "is_bkg"), 
                        exp = c("A numeric vector representing the number of points in each cluster.",
                                "A numeric value representing the number of dimensions.",
                                "A numeric value representing the number of clusters.",
                                "A numeric matrix representing the locations/centroids of clusters.",
                                "A numeric vector representing the scaling factors of clusters.",
                                "A character vector representing the shapes of clusters.",
                                "A numeric list which contains plane and the corresponding angle along that plane for each cluster.",
                                "A Boolean value representing the background noise should exist or not."))
```

@@

### Multiple cluster examples

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau"), 
                        exp = c("",
                                ""))
```

```{r odd-shape-tb-html, eval=knitr::is_html_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", col.names = c("Function", "Explanation")) 
```

```{r odd-shape-tb-pdf, eval=knitr::is_latex_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```
